---
title: "Bayesian Network - Data Science Capstone"
author: "Maxime MARTIN"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: STA 6257 - Advanced Statistical Modeling
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

## Paper review

### 1) A single Bayesian Network classifier for monitoring with unknown classes

Authors: A. Stout, A. Cohen, S. Vernon, A. Kobi.

Date: 2019

Ref : @ATOUI2019681

The authors investigate the use of BN to create a classifier for
monitoring systems with unknown classes. They employ Conditional
Gaussian Networks (CGN), where each node represents either a discrete or
Gaussian random variable linked to multivariate random variables (RV).
Their approach involves graphical analysis and a quadratic statistic to
determine the class of each multivariate observation, utilizing a
control limit (CL) for classification.

The paper delves into detailed analysis, providing insights into the
fault detection and diagnosis algorithm, including exclusion criteria.
Various structures are explored, such as simpler BN structures and their
association with CGN. The effectiveness of the proposed system is
demonstrated and evaluated using the complex Tennessee Eastman Process
(TEP).

Further research is suggested to expand the proposed approach to other
data-driven CGN, develop new algorithms to handle multiple faults, and
explore more complex BN structures for integration.

### 2) Application of Bayesian Networks in Reliability Evaluation

Authors: B. Cai, X. Kong, Y. Liu, J. Lin, X. Yuan, H. Xu, R. Ji.

Date: 2019

Ref : @Cai2020

The authors review the use of BN over the past decades, highlighting
their strengths in modeling complex systems and handling uncertainties.
Like comprehensive review of the industrial application in reliability
field. The new feature introduced in the paper is a classification
framework for BN in reliability evaluation. This
framework categorises BN based on the objects of reliability evaluation
(hardware, software), which provides a structured approach to applying
BN across various industrial contexts. This systematic classification
helps in better understanding and implementing BN for different
reliability evaluation tasks, enhancing the practical application and
effectiveness of BN in real-world scenarios.

The paper discusses various case studies, demonstrating the practical
implementation of BN in different industrial contexts. However, there
are some limitations, first the accuracy of BN heavily relies on the
availability of sufficient and high-quality data, which can be a
significant constraint. Second, applying BN to very large and complex
systems poses computational challenges, making it difficult to manage
and analyse such systems effectively. Third, there is a need for further
research to integrate BN with other reliability evaluation methods,
which could enhance their accuracy and applicability in diverse
industrial contexts. Addressing these limitations is essential for
improving the practical use of BN in reliability assessments.

### 3) Rational Irrationality: Modeling Climate Change Belief Polarization Using Bayesian Networks

Authors: J. Cook, S. Lewandowsky

Date: 2016

Ref : @JCook2016

This paper is

### 4) Quantifying and predicting the Water-Energy-Food-Economy-Society- Environment Nexus based on Bayesian networks - A case study of China

Authors: J. Chai, H. Shi, Q. Lu, Y. Hu

Date: 2020

Ref : @CHAI2020120266

This paper is about...

### 5) ...

Authors:

Date:

Ref :

This paper is

### Related work

....

## Methods

...

## Analysis and Results

...

### Data and Visualization

A study was conducted to determine how...

```{r, warning=FALSE, echo=T, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{r, warning=FALSE, echo=TRUE}
# Load Data
kable(head(murders))

ggplot1 = murders %>% ggplot(mapping = aes(x=population/10^6, y=total)) 

  ggplot1 + geom_point(aes(col=region), size = 4) +
  geom_text_repel(aes(label=abb)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(formula = "y~x", method=lm,se = F)+
  xlab("Populations in millions (log10 scale)") + 
  ylab("Total number of murders (log10 scale)") +
  ggtitle("US Gun Murders in 2010") +
  scale_color_discrete(name = "Region")+
      theme_bw()
  

```

### Statistical Modeling

```{r}

```

### Conclusion

## References
