---
title: "Bayesian Network - Data Science Capstone"
author: "Maxime MARTIN"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: STA 6257 - Advanced Statistical Modeling
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

## Paper review

### 1) A single Bayesian Network classifier for monitoring with unknown classes

Authors: A. Stout, A. Cohen, S. Vernon, A. Kobi.

Date: 2019

Ref : @ATOUI2019681

The authors investigate the use of BN to create a classifier for
monitoring systems with unknown classes. They employ Conditional
Gaussian Networks (CGN), where each node represents either a discrete or
Gaussian random variable linked to multivariate random variables (RV).
Their approach involves graphical analysis and a quadratic statistic to
determine the class of each multivariate observation, utilizing a
control limit (CL) for classification.

The paper delves into detailed analysis, providing insights into the
fault detection and diagnosis algorithm, including exclusion criteria.
Various structures are explored, such as simpler BN structures and their
association with CGN. The effectiveness of the proposed system is
demonstrated and evaluated using the complex Tennessee Eastman Process
(TEP).

Further research is suggested to expand the proposed approach to other
data-driven CGN, develop new algorithms to handle multiple faults, and
explore more complex BN structures for integration.

### 2) Application of Bayesian Networks in Reliability Evaluation

Authors: B. Cai, X. Kong, Y. Liu, J. Lin, X. Yuan, H. Xu, R. Ji.

Date: 2019

Ref : @Cai2020

The authors review the use of BN over the past decades, highlighting
their strengths in modeling complex systems and handling uncertainties.
Like comprehensive review of the industrial application in reliability
field. The new feature introduced in the paper is a classification
framework for BN in reliability evaluation. This
framework categorises BN based on the objects of reliability evaluation
(hardware, software), which provides a structured approach to applying
BN across various industrial contexts. This systematic classification
helps in better understanding and implementing BN for different
reliability evaluation tasks, enhancing the practical application and
effectiveness of BN in real-world scenarios.

The paper discusses various case studies, demonstrating the practical
implementation of BN in different industrial contexts. However, there
are some limitations, first the accuracy of BN heavily relies on the
availability of sufficient and high-quality data, which can be a
significant constraint. Second, applying BN to very large and complex
systems poses computational challenges, making it difficult to manage
and analyse such systems effectively. Third, there is a need for further
research to integrate BN with other reliability evaluation methods,
which could enhance their accuracy and applicability in diverse
industrial contexts. Addressing these limitations is essential for
improving the practical use of BN in reliability assessments.

### 3) Rational Irrationality: Modeling Climate Change Belief Polarization Using Bayesian Networks

Authors: J. Cook, S. Lewandowsky

Date: 2016

Ref : @JCook2016

This paper examines belief polarization, which occurs when two
individuals interpret the same evidence and update their beliefs in
opposite directions. This phenomenon represents the irrational aspect of
the study. The researchers use Bayesian networks to simulate belief
polarization, representing the rational aspect.

The study focuses on climate change beliefs in two countries, Australia
and the USA. Four groups of variables were used to illustrate different
factors: W (worldview/free market support), T (trust in climate
scientists), H (belief in human-caused global warming), and E (evidence
from scientific consensus). The relationships between these variables
are modeled as follows: W-T, W-H, T-E, H-E.

The aim was to determine if individuals with different worldviews (W)
exhibit belief polarization when presented with scientific evidence,
considering varying levels of trust in climate scientists and belief in
human-caused global warming.

Data analysis was conducted using R, modeling ANOVA tests for each
variable combination. Significant differences were found between the two
countries. Bayesian networks were then fitted to each country's data,
resulting in unique sets of Bayesian network parameters for each.

The study found that worldview is a dominant influence on climate
beliefs and that providing consensus information increases the
perception of consensus. Among U.S. participants, the consensus
intervention led to increased distrust in scientists among those with a
particular worldview when informed about the scientific consensus.

A limitation of the study is the small effect sizes of the experimental
manipulation compared to the large effect of worldview, which may be due
to the brief nature of the manipulation.

### 4) \*\*\* Quantifying and predicting the Water-Energy-Food-Economy-Society- Environment Nexus based on Bayesian networks - A case study of China

Authors: J. Chai, H. Shi, Q. Lu, Y. Hu

Date: 2020

Ref : @CHAI2020120266

This paper is about...

### 5) Applications of Bayesian networks and Petri nets in safety, reliability, and risk assessments: A review

Authors: S. Kabir, Y. Papadopoulos

Date: 2019

Ref : @KABIR2019154

This paper is a review of how to prevent risk by controlling the
parameter of reliability and risk assessments in complex systems by
using Bayesian networks and Petri nets. Even if half of the paper will
be on petri nets, it's interesting to see the link between those two
methods. We can also mention the use of markov chain to do the same
surveillance. It also explain the links between other methods to
Bayesian networks, for example how to go from a fault tree to a Bayesian
network (the mapping process).

It's re-explaining the advantages of Bayesian networks and why using
them in a problem related to safety and risk assessment. The main
advantage of Bayesian networks over the other existing approaches is
their polyvalency, they can offer different functionality such as
predictive and diagnostic analysis model, updating, and optimization.
Also, Bayesian network can applied both discrete and continuous model of
time.

They also explain the process of creation of a Bayesian network,
following these steps:

I. Identify variables -\> identify network structure -\> Express as
statistical variables

II\. Specify conditional probabilities

III\. Enter evidence -\> Propagate -\> Interprete results

The major limitations of Bayesian network aplications are that the
guideline we use to create the nodes will define the result at the end,
so to ensure a coherent model we should take care of the few first
steps. Also, if the parent-child relationships are not properly defined,
the model can be more complex to analyse.

### Related work

....

## Methods

...

## Analysis and Results

...

### Data and Visualization

A study was conducted to determine how...

```{r, warning=FALSE, echo=F, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
library(bnlearn)
```

### Loading the data

```{r, warning=FALSE, echo=TRUE}
asia<- bnlearn::asia
```

### Writing the model

Rearanging the data and plotting the relationship between the
parameters.

```{r}
colnames(asia) <- c("VisittoAsia","Smoking","Tuberculosis","LungCancer","Bronchitis", "TuberculosisCersusLungCancer_Bronchitis",
                      "ChestXray","Dyspnoea")

bn_df <- data.frame(asia)
res <- hc(bn_df)
plot(res)
```

### Rewrite the model and plot it

We will rewrite the model with new informations we have. And we will
plot again the results.

```{r}
res = model2network("[VisittoAsia][Smoking][Tuberculosis|VisittoAsia][LungCancer|Smoking][Bronchitis|Smoking][Dyspnoea|Bronchitis:TuberculosisCersusLungCancer_Bronchitis][TuberculosisCersusLungCancer_Bronchitis|Tuberculosis:LungCancer][ChestXray|TuberculosisCersusLungCancer_Bronchitis]")

#res <- hc(bn_df)
plot(res)
```

Visit to asia is alone, means that there is nothing pointed to it. Same
for Smoking because it's only a parent node.

Tuberculosis\|VisittoAsia means that Tuberculosis is influenced by visit
to asia.

etc .. etc...

### Fit the model to our data

Now we will fit the model we have to our data

```{r}
fittedbn <- bn.fit(res, data = bn_df)

graphviz.chart(
  fittedbn,
  type = "barprob" ,
  layout = "fdp",
  scale = c(0.75, 0.9),
  grid = TRUE,
  bar.col = "red",
  strip.bg = "lightskyblue"
)
```

```{r}
fittedbn <- bn.fit(res, data = bn_df)

print(fittedbn$Tuberculosis)
print(fittedbn$TuberculosisCersusLungCancer_Bronchitis)
```

```{r}
cpquery(fittedbn, event = (Smoking=="yes"), evidence = (Bronchitis=="no"))
print(fittedbn$Tuberculosis)
fittedbn[["Bronchitis"]]
```

```{r}

```

### Statistical Modeling

```{r}

```

### Conclusion

## References
